---
title: "Titanic_Kaggle"
author: "GHEZAIEL Morad"
date: "06/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(factoextra)
library(FactoMineR)
library(stringr)
library(ica)
library(gridExtra)
library(corrplot)
library(cluster)
library(plotly)
```

# Path init 
```{r}
path = "/home/jaz/PycharmProjects/DS/Titanic/titanic/"
train_path = paste0(path,"train.csv")
test_path = paste0(path,"test.csv")
sub_path = paste0(path,'gender_submission.csv')
```

# Load data 
```{r}
train = read.csv(train_path)
test = read.csv(test_path)
sub = read.csv(sub_path)
train
test
sub
```

# Processing 

## Feature extraction

### We first look for NA values 

```{r}
na.rows = which(is.na(train)==TRUE)
for(i in 1:length(train))
{
  print(names(train)[i])
  print(anyNA(train[,i]))
}
```

It seems that only the age feature contains na values. 
We will later perform clustering on the remaining features and impute the missing data accordingly. 

But first, let's digitize the data matrix 

```{r}
processed = train 
processed$Sex = as.integer(processed$Sex)
processed$Embarked = as.integer(processed$Embarked)
```

There is 3 string like feature: 
- Passenger name 
- Ticket ID 
- Cabin ID 

We will process it independantly, 

### Passenger name processing
To encode names as numeric features, we will consider a bag of syllabs 
and will one-hot encode their presence in passengers names. 

```{r}
# One hot encode syllabs occurences
syllabs = c("on","ey","en","field","ing","ee","an","er","ard","Mc","k","w","am","sk",'"','[)]')
df = data.frame(id = 1:dim(train)[1])
for(i in 1:length(syllabs))
{
 syl = syllabs[i]
 is_present = sapply(train$Name,function(x){if(str_detect(x,syl)==TRUE){1} else{0}})
 df = cbind(df,is_present)
}
names(df) = c("id",syllabs)

# Data viz 
df = df[,2:length(df)]
ggplot(data.frame(colSums(df)),aes(x=reorder(colnames(df),colSums(df)),y=colSums(df)))+
  geom_col(stat='identity',fill="lightblue",color="white")+
  xlab("Syllab in passengers names")+
  ylab("Frequency")


```

Then we make sure that our bag of syllabs cover the entire Name space
```{r}
df[rowSums(df)==0,]
```




### Ticket id processing 

It appears that this feature is composed by strings and numbers. 
Also, strings are composed by characters prefixs followed by a number. 
Some prefix are redondant, some others are not. 

For numbers, we will assume that they are not quantitative variables. 
Instead, we will take account of their length and their parity.

In that way, we will encode this feature as following: 
- Presence of a prefix (A)
- Presence of backslash in the prefix (B)
- Presence of dot in the prefix (C)
- Length of the character prefix (D)
- Length of the number id (E)
- Parity of the number id (F)

```{r}
# We use regular expression for that task
A = sapply(train$Ticket, function(x){str_detect(x,"[a-zA-Z]")})
B = sapply(train$Ticket, function(x){str_detect(x,"[/]")})
C = sapply(train$Ticket, function(x){str_detect(x,"[.]")})
D = sapply(train$Ticket, function(x){length(unlist(str_extract_all(x,"[a-zA-Z./]")))})
E = sapply(train$Ticket, function(x){str_length(unlist(str_extract(x,"[0-9]{2,12}")))})
F = as.integer(unlist(str_extract(train$Ticket,"[0-9]{2,12}")))%%2==0

# Impute NA with most common
D[is.na(D)]<-mean(D)
E[is.na(E)]<-names(sort(table(E)))[length(table(E))]
F[is.na(F)]<-FALSE

# Digitize
A = as.integer(A)
B = as.integer(B)
C = as.integer(C)
E = as.integer(E)
F = as.integer(F)

# Data viz
ticket = data.frame(has.prefix =A, has.backslash =B, has.dot = C, is.pair=F)
p1 <- ggplot(data.frame(colSums(ticket)),aes(x=reorder(colnames(ticket),colSums(ticket)),y=colSums(ticket)/dim(ticket)[1]))+
  geom_col(fill="lightblue",color="white")+
  xlab("Features")+
  ylab("Frequency")
p2 <- ggplot(data.frame(D=D),aes(D))+geom_histogram(bins=5,fill="blue",color="white")+xlab("Prefix length")
p3 <- ggplot(data.frame(E=E),aes(E))+geom_histogram(bins=5,fill="darkblue",color="white")+xlab("Number length")
grid.arrange(p1,p2,p3,ncol=2)+theme_grey()
```

### Cabin ID processing 

This feature is composed by strings and white spaces. 
Some passengers are given more than 1 cabin.
Conversly, some are not given any cabin. 

Similarly to the ticket feature, we will encode this one as following: 

- Has at least one cabin (G)
- Number of cabins (H)
- Cabin letter (I)

We could consider more encoded feature such as consecutivness of cabins or parity, but we will keep it simple. 

```{r}
G = sapply(train$Cabin, function(x){str_detect(x,"[^a-zA-Z0-9]")})
H = sapply(train$Cabin, function(x){length(unlist(str_extract_all(x,"[a-zA-Z0-9]+")))})
I = sapply(train$Cabin, function(x){unlist(str_extract_all(x,"[a-zA-Z]"))})
I = unlist(lapply(I,function(x)(if("A" %in% x){1}
                         else if("B" %in% x){2}
                         else if("C" %in% x){3}
                         else if("D" %in% x){4}
                         else if("E" %in% x){5}
                         else if("F" %in% x){6}
                         else if("G" %in% x){7}
                         else {0}
                         )))
G = as.integer(G)
p1 <- ggplot(data.frame(G=G),aes(x = sapply(G,function(x){if(x==0){"No"}else{"Yes"}})))+geom_bar(fill="lightblue",color="white")+xlab("Has at least one cabin")
p2 <- ggplot(data.frame(H=H),aes(H))+geom_histogram(bins=5,fill="blue",color="white")+xlab("Number of cabins")
p3 <- ggplot(data.frame(I=I),aes(I))+geom_histogram(bins=5,fill="darkblue",color="white")+xlab("Floor")
grid.arrange(p1,p2,p3,ncol=2)+theme_grey()

```

Now, lets create a new dataframe to store our extracted features and the other ones. 

```{r}
# Add extracted features
df.extracted = data.frame(id = train$PassengerId)
df.extracted = cbind(df.extracted,df[,2:length(df)])
df.extracted$A = A
df.extracted$B = B 
df.extracted$C = C 
df.extracted$D = D 
df.extracted$E = E 
df.extracted$F = F 
df.extracted$G = G 
df.extracted$H = H 
df.extracted$I = I 

# Merge with the initial dataframe
df.extracted = cbind(df.extracted,processed)

# Remove the old features and digitize some
df.extracted$id = NULL 
df.extracted$Name = NULL
df.extracted$Ticket = NULL 
df.extracted$Cabin = NULL 
df.extracted$Embarked = as.integer(df.extracted$Embarked)

# Store the label 
label = train$Survived

# Store the na containing feature 
na.age = df.extracted$Age
df.extracted$Age = NULL

# Store the passenger id label 
p.id = df.extracted$PassengerId
df.extracted$PassengerId = NULL
```

## Feature engineering

In this step, we will produce more features with the aim to facilitate 
the classification task. 

"Womens and kids before". This sentence may inform us on the importance of the sex and age features. 

As evoked previously the age of the passengers appears to contain NA values. 
To overcome this problem, we will impute the vector according to a clustering label. 

We first need to find which features positively correlate with surviveness. 
Then, we will combine these features to produce a relevant variable space for clustering and further imputation. 

### Correlation
```{r}
df.extracted$label = label
cormat = cor(df.extracted)
curr = data.frame(cormat)
corrplot(cormat,tl.cex=0.7)
```

A common problem in feature engineering is the presence of null values which cannot be divided or multiplied (in an information conservation context). 

To overcome this, we simply add 1 to the whole dataset. 

```{r}
df.extracted$label = NULL 
df.extracted = df.extracted+1
```

Then, we will combine the features according to the correlation plot: 
1) Find features that are highly absolutely correlated with survivness (main features)
2) Find features that highly absolutely correlated with the main features and combine them (secondary features)
3) Then, combine secondary features with their respective main features (resulting feature)
4) Combine resulting features from each main features together 


<b>Main features:
    Secondary features:</b>
    
- Sex: 
    - Pclass,I,H, Parch,Fare
- Pclass: 
    - I,H, Fare,Embarked
- I: 
    - H, ), er, B, C, Fare,Embarked
- H: 
    - G, er, B, C, Fare,Embarked,Parch
- G: 
    - er,ard,field,Fare,Parch,I,Pclass
- (:
    - k,w,am,sk,er,ing,field,en,ey,on,sex,parch,I,pclass,"
- ":
    - en,(,sex
- er: 
  - Fare,parch,sibsp,pclass
  

We then compute correlation of these feature with survivness and filter interesting ones


The results indicates several groups of correlated features. 
Not very visible, but the last row/col is the label, it appears to be absolutely correlated 
to our engineered features, that's what we looked for ! 

### Age imputation 

With a relevant variable space, we can now try to impute the NA containing feature. 
As evoked previously, we will perform clustering to identify group of individuals. 
Then, we will impute the concerned individuals within their own clusters. 

First, we perform principal component analysis on unscaled data 

```{r}
# Merge the original dataset with the feature augmented 
df_tocluster = df.extracted
#df_engineered$label = NULL
df_tocluster$f2 = NULL
res.pca = PCA(df_tocluster,ncp = 3) 
comps = data.frame(res.pca$ind$coord)
ggplot(comps,aes(Dim.1,Dim.2,color=factor(label)))+geom_point()
ggplot(comps,aes(Dim.1,Dim.3,color=factor(label)))+geom_point()
ggplot(comps,aes(Dim.2,Dim.3,color=factor(label)))+geom_point()

```
 
Clusters are quite fuzzy, but the first component appears to be able to separate the two clusters. 
Conversly, the second dimensions appears to be responsible to the fuzzy structure
Let's subset the variable space to those with no or very low contribution to the second axis

```{r}
df_tocluster$A = NULL
df_tocluster$B = NULL 
df_tocluster$C = NULL 
df_tocluster$D = NULL
res.pca = PCA(df_tocluster,ncp = 3) 
comps = data.frame(res.pca$ind$coord)
ggplot(comps,aes(Dim.1,Dim.2,color=factor(label)))+geom_point()
ggplot(comps,aes(Dim.1,Dim.3,color=factor(label)))+geom_point()
ggplot(comps,aes(Dim.2,Dim.3,color=factor(label)))+geom_point()


km.out = kmeans(df_tocluster,centers=10,nstart =20)

ggplot(comps,aes(Dim.1,Dim.2,color=factor(km.out$cluster)))+geom_point()
ggplot(comps,aes(Dim.1,Dim.3,color=factor(km.out$cluster)))+geom_point()
ggplot(comps,aes(Dim.2,Dim.3,color=factor(km.out$cluster)))+geom_point()
```

```{r}
contribs = data.frame(res.pca$var$coord)
contribs
plot(contribs$Dim.1)
plot(contribs$Dim.2)
plot(contribs$Dim.3)
```


```{r}
df_tocluster$k = NULL
res.pca = PCA(df_tocluster,ncp = 3) 
comps = data.frame(res.pca$ind$coord)
ggplot(comps,aes(Dim.1,Dim.2,color=factor(label)))+geom_point()
ggplot(comps,aes(Dim.1,Dim.3,color=factor(label)))+geom_point()
ggplot(comps,aes(Dim.2,Dim.3,color=factor(label)))+geom_point()


km.out = kmeans(df_tocluster,centers=10,nstart =20)

ggplot(comps,aes(Dim.1,Dim.2,color=factor(km.out$cluster)))+geom_point()
ggplot(comps,aes(Dim.1,Dim.3,color=factor(km.out$cluster)))+geom_point()
ggplot(comps,aes(Dim.2,Dim.3,color=factor(km.out$cluster)))+geom_point()
```

```{r}
contribs = data.frame(res.pca$var$coord)
contribs
plot(contribs$Dim.1)
plot(contribs$Dim.2)
plot(contribs$Dim.3)
```


```{r}
f2 = mapply(function(x,y){x*y}, df_tocluster$Parch, df_tocluster$SibSp)
df_tocluster$f2 = f2
```

```{r}
res.pca = PCA(df_tocluster,ncp = 3) 
comps = data.frame(res.pca$ind$coord)
ggplot(comps,aes(Dim.1,Dim.2,color=factor(label)))+geom_point()
ggplot(comps,aes(Dim.1,Dim.3,color=factor(label)))+geom_point()
ggplot(comps,aes(Dim.2,Dim.3,color=factor(label)))+geom_point()


km.out = kmeans(df_tocluster,centers=10,nstart =20)

ggplot(comps,aes(Dim.1,Dim.2,color=factor(km.out$cluster)))+geom_point()
ggplot(comps,aes(Dim.1,Dim.3,color=factor(km.out$cluster)))+geom_point()
ggplot(comps,aes(Dim.2,Dim.3,color=factor(km.out$cluster)))+geom_point()
```

# To do: impute missing according to mean in cluster 


```{r}
train$Age
for(i in 1:length(train$Age))
{
  if(is.na(train$Age[i]) | is.nan(train$Age[i]))
  {
    label = km.out$cluster[i]
    target = train$Age[which(km.out$cluster==label)]
    print(mean(na.omit(target)))
    train$Age[i] <- mean(na.omit(target))
  }
}
train$Age
```

```{r}
df_tocluster$Age = train$Age
df_tocluster = na.omit(df_tocluster)
label = train$Survived
label = label[!is.na(train$Age)]
```

Now, lets perform PCA another time to get insight into age contribution


```{r}
res.pca = PCA(df_tocluster,ncp = 3) 
comps = data.frame(res.pca$ind$coord)
ggplot(comps,aes(Dim.1,Dim.2,color=factor(label)))+geom_point()
ggplot(comps,aes(Dim.1,Dim.3,color=factor(label)))+geom_point()
ggplot(comps,aes(Dim.2,Dim.3,color=factor(label)))+geom_point()


km.out = kmeans(df_tocluster,centers=10,nstart =20)

ggplot(comps,aes(Dim.1,Dim.2,color=factor(km.out$cluster)))+geom_point()
ggplot(comps,aes(Dim.1,Dim.3,color=factor(km.out$cluster)))+geom_point()
ggplot(comps,aes(Dim.2,Dim.3,color=factor(km.out$cluster)))+geom_point()
```

Now, let's perform the same process but for the test set 

```{r}
na.rows = which(is.na(test)==TRUE)
for(i in 1:length(test))
{
  print(names(test)[i])
  print(anyNA(test[,i]))
}
```

Same as previously, only the age feature contains NA values 

```{r}
processed = test 
processed$Sex = as.integer(processed$Sex)
processed$Embarked = as.integer(processed$Embarked)
```

```{r}
# One hot encode syllabs occurences
syllabs = c("on","ey","en","field","ing","ee","an","er","ard","Mc","k","w","am","sk",'"','[)]')
df = data.frame(id = 1:dim(test)[1])
for(i in 1:length(syllabs))
{
 syl = syllabs[i]
 is_present = sapply(test$Name,function(x){if(str_detect(x,syl)==TRUE){1} else{0}})
 df = cbind(df,is_present)
}
names(df) = c("id",syllabs)

```

```{r}
# We use regular expression for that task
A = sapply(test$Ticket, function(x){str_detect(x,"[a-zA-Z]")})
B = sapply(test$Ticket, function(x){str_detect(x,"[/]")})
C = sapply(test$Ticket, function(x){str_detect(x,"[.]")})
D = sapply(test$Ticket, function(x){length(unlist(str_extract_all(x,"[a-zA-Z./]")))})
E = sapply(test$Ticket, function(x){str_length(unlist(str_extract(x,"[0-9]{2,12}")))})
F = as.integer(unlist(str_extract(test$Ticket,"[0-9]{2,12}")))%%2==0

# Impute NA with most common
D[is.na(D)]<-mean(D)
E[is.na(E)]<-names(sort(table(E)))[length(table(E))]
F[is.na(F)]<-FALSE

# Digitize
A = as.integer(A)
B = as.integer(B)
C = as.integer(C)
E = as.integer(E)
F = as.integer(F)
```

```{r}
G = sapply(test$Cabin, function(x){str_detect(x,"[^a-zA-Z0-9]")})
H = sapply(test$Cabin, function(x){length(unlist(str_extract_all(x,"[a-zA-Z0-9]+")))})
I = sapply(test$Cabin, function(x){unlist(str_extract_all(x,"[a-zA-Z]"))})
I = unlist(lapply(I,function(x)(if("A" %in% x){1}
                         else if("B" %in% x){2}
                         else if("C" %in% x){3}
                         else if("D" %in% x){4}
                         else if("E" %in% x){5}
                         else if("F" %in% x){6}
                         else if("G" %in% x){7}
                         else {0}
                         )))
G = as.integer(G)
```

```{r}
# Add extracted features
df.extracted_test = data.frame(id = test$PassengerId)
df.extracted_test = cbind(df.extracted_test,df[,2:length(df)])
df.extracted_test$A = A
df.extracted_test$B = B 
df.extracted_test$C = C 
df.extracted_test$D = D 
df.extracted_test$E = E 
df.extracted_test$F = F 
df.extracted_test$G = G 
df.extracted_test$H = H 
df.extracted_test$I = I 

# Merge with the initial dataframe
df.extracted_test = cbind(df.extracted_test,processed)

# Remove the old features and digitize some
df.extracted_test$id = NULL 
df.extracted_test$Name = NULL
df.extracted_test$Ticket = NULL 
df.extracted_test$Cabin = NULL 
df.extracted_test$Embarked = as.integer(df.extracted_test$Embarked)
```

```{r}
# Store the na containing feature 
na.age = df.extracted_test$Age
df.extracted_test$Age = NULL

# Store the passenger id label 
p.id = df.extracted_test$PassengerId
df.extracted_test$PassengerId = NULL
```

```{r}
df.extracted_test$label = NULL 
df.extracted_test = df.extracted_test+1
```


# Age imputation 

```{r}
# Merge the original dataset with the feature augmented 
df_tocluster_test = df.extracted_test
df_tocluster_test$f2 = NULL
res.pca = PCA(df_tocluster_test,ncp = 3) 
comps = data.frame(res.pca$ind$coord)
ggplot(comps,aes(Dim.1,Dim.2))+geom_point()
ggplot(comps,aes(Dim.1,Dim.3))+geom_point()
ggplot(comps,aes(Dim.2,Dim.3))+geom_point()
```

```{r}
df_tocluster_test$A = NULL
df_tocluster_test$B = NULL 
df_tocluster_test$C = NULL 
df_tocluster_test$D = NULL
df_tocluster_test$k = NULL
f2 = mapply(function(x,y){x*y}, df_tocluster_test$Parch, df_tocluster_test$SibSp)
df_tocluster_test$f2 = f2


res.pca = PCA(df_tocluster_test,ncp = 3) 
comps = data.frame(res.pca$ind$coord)
ggplot(comps,aes(Dim.1,Dim.2))+geom_point()
ggplot(comps,aes(Dim.1,Dim.3))+geom_point()
ggplot(comps,aes(Dim.2,Dim.3,))+geom_point()



```
There is one individual for which the Fare feature is na
```{r}
km.out = kmeans(df_tocluster_test[,which(colnames(df_tocluster_test)!="Fare")],centers=10,nstart =20)

ggplot(comps,aes(Dim.1,Dim.2,color=factor(km.out$cluster)))+geom_point()
ggplot(comps,aes(Dim.1,Dim.3,color=factor(km.out$cluster)))+geom_point()
ggplot(comps,aes(Dim.2,Dim.3,color=factor(km.out$cluster)))+geom_point()
```

```{r}
for(i in 1:length(test$Age))
{
  if(is.na(test$Age[i]))
  {
    label = km.out$cluster[i]
    target = test$Age[which(km.out$cluster==label)]
    curr = na.omit(test$Age)
    test$Age[i]<- mean(curr)
  }
}
df_tocluster_test$Age = test$Age
```

```{r}
sort(colnames(df_tocluster_test))
```
```{r}
sort(colnames(df_tocluster))
```


```{r}
for(i in 1:length(df_tocluster_test))
{
  print(colnames(df_tocluster_test)[i])
  print(which(is.na(df_tocluster_test[,i])==TRUE))
}
```

```{r}
label = df_tocluster$Survived
df_tocluster$Survived = NULL
df_tocluster_test$on = NULL
```

```{r}
df_tocluster$label = label
df_tocluster_test$ID = test$PassengerId
write.csv(df_tocluster,"train_titanic.csv")
write.csv(df_tocluster_test,"test_titanic.csv")
```

